---
title: "Findbeta extensions ver1"
author: "Konstantinos Pateras"
date: "2022-12-09"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Candidates for  inclusion in priorGen()

## Summary of candidate functions
* Updated basic findbeta (original function with percentiles)
    + Mean, Median, Mode
* Raw findbeta (standard location and scale measures (mean,median,mode,variance,range))
    + Mean, Median, Mode
* Abstract findbeta (general statements of how low/high are the mean and variance)
    + Mean
* Panel findbeta (Multiple experts or sources of information contribute to define this prior, based on simple averaging)
    + Mean, Median, Mode


\newpage
## Updated basic findbeta
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta.r")
findbeta(themedian = 0.5,lower.v = T,percentile = 0.999,percentile.value = 0.999, silent = F)
#findbeta(themode = 0.5,lower.v = T,percentile = 0.80,percentile.value = 0.95, silent = T)
fb_per=findbeta(themean = 0.5,lower.v = T,percentile = 0.90,percentile.value = 0.95, silent = T)
fb_per$parameters
fb_per$summary
fb_per$input
```

\newpage
## Raw findbeta (mean/median/mode/variance/range input)
```{r include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_raw.r")
findbeta_raw(themedian = 0.5,therange = c(0,1), silent = T)
#findbeta_raw(themode = 0.5,therange = c(0,1), silent = T)
fb_raw=findbeta_raw(themean = 0.8,thevariance = 0.2,silent = T)
fb_raw$parameters
fb_raw$summary
fb_raw$input
```

\newpage
## Abstract findbeta (General statements input)
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_abstract.r")
findbeta_abstract(themean.cat = "Low",thevariance.cat = "High", silent = T) 
#findbeta_abstract(themean.cat = "Very low",thevariance.cat = "Low", silent = T) 
fb_abstract=findbeta_abstract(themean.cat =  "Low",thevariance.cat = "High",silent = T)
fb_abstract$parameters
fb_abstract$summary
fb_abstract$input
```
\newpage
## Panel findbeta (Vector input)
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_panel.r")
#findbeta_panel(themedian.vec = c(0.2,0.02,0.5,0.03,0.04,0.05),silent = T) 
findbeta_panel(themode.vec = c(0.2,0.02,0.5,0.03,0.04,0.05),silent = F) 
fb_panel=findbeta_panel(themean.vec = c(0.2,0.02,0.5,0.03,0.04,0.05),silent = T) 
fb_panel$parameters
fb_panel$summary
fb_panel$input
```

\newpage
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_plot.r")
fb_pr=findbeta(themean = 0.5,lower.v = T,percentile = 0.999,percentile.value = 0.999,silent = T) 
findbeta_plot(fb_pr,main="Elicited beta prior (Percentile)",ylab = "Density",lwd=3,type="l")
```
\newpage
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_plot.r")
fb_raw=findbeta_raw(themean = 0.5,thevariance = 0.5) 
findbeta_plot(fb_raw,main="Elicited beta prior (Raw)",ylab = "Density",lwd=3,type="l")
```
\newpage
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_plot.r")
fb_abstract=findbeta_abstract(themean.cat = "Low",thevariance.cat = "High") 
findbeta_plot(fb_abstract,main="Elicited beta prior (Abstract)",ylab = "Density",lwd=3,type="l")
```
\newpage
```{r  include=TRUE}
source("~/GitHub/PriorGen-1/R/findbeta_plot.r")
fb_panel1=findbeta_panel(themean.vec = c(0.2,0.02,0.5,0.03,0.04,0.05),silent = T) 
fb_panel2=findbeta_panel(themean.vec = c(0.2,0.02,0.5,0.4,0.04,0.05),silent =T) 
findbeta_plot(fb_panel1,main="Elicited beta prior  (Panel)",ylab = "Density",lwd=3,type="l")
findbeta_plot(fb_panel2,lwd=3,type="l",lines = T)
```
