---
title: "PriorGen old/new features ver 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PriorGen old/new features ver 1}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\newpage
## Basic findbeta updated
```{r  include=TRUE}
library(PriorGen)
findbeta(themedian = 0.5,lower.v = T,percentile = 0.999,percentile.value = 0.999)
#findbeta(themode = 0.5,lower.v = T,percentile = 0.80,percentile.value = 0.95)
fb_per=findbeta(themean = 0.5,lower.v = T,percentile = 0.90,percentile.value = 0.95)
fb_per$parameters
fb_per$summary
fb_per$input
```
\newpage
## Raw findbeta (mean/median/mode/variance/range input)
```{r include=TRUE}
library(PriorGen)
findbeta_raw(themedian = 0.5,therange = c(0,1))
#findbeta_raw(themode = 0.5,therange = c(0,1))
fb_raw=findbeta_raw(themean = 0.8,thevariance = 0.2)
fb_raw$parameters
fb_raw$summary
fb_raw$input
```
\newpage
## Abstract findbeta (General statements input)
```{r  include=TRUE}
library(PriorGen)
findbeta_abstract(themean.cat = "Low",thevariance.cat = "High") 
#findbeta_abstract(themean.cat = "Very low",thevariance.cat = "Low") 
fb_abstract=findbeta_abstract(themean.cat =  "Low",thevariance.cat = "High")
fb_abstract$parameters
fb_abstract$summary
fb_abstract$input
```
\newpage
## Panel findbeta (Vector input)
```{r  include=TRUE}
library(PriorGen)
#findbeta_panel(themedian.vec = c(0.2,0.02,0.5,0.03,0.04,0.05)) 
findbeta_panel(themode.vec = c(0.2,0.02,0.5,0.03,0.04,0.05)) 
fb_panel=findbeta_panel(themean.vec = c(0.2,0.02,0.5,0.03,0.04,0.05)) 
fb_panel$parameters
fb_panel$summary
fb_panel$input
```
\newpage
## Basic findbetaqq updated (Percentiles input)
```{r  include=TRUE}
library(PriorGen)
fb_qq=findbetaqq(percentile.value1 = 0.3,percentile1 = 0.20,
                 percentile.value2 = 0.7,percentile2 = 0.97) 
fb_qq$parameters
fb_qq$summary
fb_qq$input
```
\newpage
## Basic findbetamupsi updated (Hierarchical input  + choice of root function)
```{r  include=TRUE}
library(PriorGen)
fb_mupsi_RS=findbetamupsi(themean=0.20, percentile=0.99, lower.v=TRUE,
              percentile.value=0.30, psi.percentile=0.90,
              percentile.median=0.60, percentile95value=0.80,root.method="multiroot")
fb_mupsi_RS$parameters
fb_mupsi_RS$summary
fb_mupsi_RS$input

fb_mupsi_NL=findbetamupsi(themean=0.20, percentile=0.99, lower.v=TRUE,
              percentile.value=0.30, psi.percentile=0.90,
              percentile.median=0.60, percentile95value=0.80,root.method="nleqslv")
fb_mupsi_RS$parameters
fb_mupsi_NL$parameters
# Results are similar

```
\newpage
## Raw findbetamupsi updated (Hierarchical input)
```{r  include=TRUE}
library(PriorGen)
fb_mupsi_raw=findbetamupsi_raw(themean=0.20,thevariance = 0.05, thepsi=0.15)
fb_mupsi_raw$parameters
fb_mupsi_raw$summary
fb_mupsi_raw$input
```
\newpage
## Abstract findbetamupsi updated (Hierarchical input)
```{r  include=TRUE}
library(PriorGen)
fb_mupsi_abstract=findbetamupsi_abstract(themean="Average",thevariance = "Very high", 
                                         psi.percentile=0.90,percentile.median=0.999,
                                         percentile95value=0.9999)
fb_mupsi_abstract$parameters
fb_mupsi_abstract$summary
fb_mupsi_abstract$input
```
\newpage
## Panel findbetamupsi updated (Hierarchical input)
```{r  include=TRUE}
library(PriorGen)
fb_mupsi_panel=findbetamupsi_panel(themean=c(0.1,0.5,0.6,0.3,0.05,0.01,0.3), 
                                   psi.percentile=0.90, percentile.median=0.50,
                                   percentile95value=0.60)
fb_mupsi_panel$parameters
fb_mupsi_panel$summary
fb_mupsi_panel$input

```
\newpage 
# Plot for findbeta
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_pr=findbeta(themean = 0.5,lower.v = T,percentile = 0.999,percentile.value = 0.999) 
plot(fb_pr,main="Elicited beta prior \n(Percentile)",ylab = "Density",lwd=3,type="l",xlab="")
```
\newpage
# Plot for finbeta_raw
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_raw=findbeta_raw(themean = 0.5,thevariance = 0.5) 
plot(fb_raw,main="Elicited beta prior \n(Raw)",ylab = "Density",lwd=3,type="l",xlab="")
```
\newpage
# Plot for findbeta_abstract
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_abstract=findbeta_abstract(themean.cat = "Low",thevariance.cat = "High") 
plot(fb_abstract,main="Elicited beta prior \n(Abstract)",ylab = "Density",lwd=3,type="l",xlab="")
```
\newpage

# Plot for findbeta_panel
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_panel1=findbeta_panel(themean.vec = c(0.2,0.02,0.5,0.03,0.04,0.05)) 
fb_panel2=findbeta_panel(themean.vec = c(0.2,0.02,0.5,0.4,0.04,0.05)) 
plot(fb_panel1,main="Elicited beta prior  \n(Panel)",ylab = "Density",lwd=3,type="l",xlab="")
lines(fb_panel2,lwd=3,type="l",lty=2)
legend("topright",c("Panel 1", "Panel 2"),lty = c(1,2),lwd=3)
```
\newpage

# Plot for findbetaqq
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)

fb_qq=findbetaqq(percentile.value1 = 0.3,percentile1 = 0.20,
percentile.value2 = 0.7,percentile2 = 0.97) 

plot(fb_qq,main="Elicited beta prior \n(Percentiles method)",ylab = "Density",lwd=3,type="l",xlab="")
```
\newpage

# Plots for finbetamupsi
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_mupsi=findbetamupsi(themean=0.20, percentile=0.99, lower.v=TRUE,
              percentile.value=0.30, psi.percentile=0.90,
              percentile.median=0.50, percentile95value=0.60)
#par(mfrow=c(1,3))
#plot(density(fb_mupsi$param_upper$at),lwd=3,main="Density plot for samples of a=mu*psi") # 
#plot(density(fb_mupsi$param_upper$bt),lwd=3,main="Density plot for samples of b=mu*(1-psi)") # 
plot(fb_mupsi,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",xlab="")
fb_mupsi1=findbetamupsi(themean=0.30, percentile=0.8, lower.v=TRUE,
              percentile.value=0.30, psi.percentile=0.90,
              percentile.median=0.70, percentile95value=0.80)
lines(fb_mupsi1,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",lty=2,col="gray")
legend("topright",c("Basic","Basic1"),col=c("black","gray"),lty=1:2,lwd=3)

```
\newpage

# Plots for findbetamupsi_raw
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_mupsi_raw=findbetamupsi_raw(themean=0.20, thevariance = 0.1, thepsi=0.15)
#par(mfrow=c(1,3))
#plot(density(fb_mupsi_abstract$param_upper$at),lwd=3,main="Density plot for samples of a=mu*psi") # 
#plot(density(fb_mupsi_abstract$param_upper$bt),lwd=3,main="Density plot for samples of b=mu*(1-psi)") # 
plot(fb_mupsi_raw,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",xlab="")
fb_mupsi_raw1=findbetamupsi_raw(themean=0.30, thevariance = 0.15, thepsi=0.15)
lines(fb_mupsi_raw1,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",lty=2,col="gray")
legend("topright",c("Raw","Raw1"),col=c("black","gray"),lty=1:2,lwd=3)
```
\newpage

# Plots for findbetamupsi_abstract
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_mupsi_abstract=findbetamupsi_abstract(themean="Low", thevariance = "High", 
psi.percentile=0.90, percentile.median=0.95, percentile95value=0.98)
#par(mfrow=c(1,3))
#plot(density(fb_mupsi_abstract$param_upper$at),lwd=3,main="Density plot for samples of a=mu*psi") # 
#plot(density(fb_mupsi_abstract$param_upper$bt),lwd=3,main="Density plot for samples of b=mu*(1-psi)") # 
plot(fb_mupsi_abstract,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",xlab="")
fb_mupsi_abstract1=findbetamupsi_abstract(themean="Very low", thevariance = "Average",
                                          psi.percentile=0.90,percentile.median=0.95, 
                                          percentile95value=0.98)
lines(fb_mupsi_abstract1,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",lty=2,col="gray")
legend("topright",c("Abstract","Abstract1"),col=c("black","gray"),lty=1:2,lwd=3)

```
\newpage

# Plots for findbetamupsi_panel
```{r  fig.align='center', out.width = "500px", dpi=300, include=TRUE}
library(PriorGen)
fb_mupsi_panel=findbetamupsi_panel(themean=c(0.1,0.5,0.05,0.01,0.4,0.2), psi.percentile=0.90,
                                   percentile.median=0.50, percentile95value=0.60)
#par(mfrow=c(1,3))
#plot(density(fb_mupsi_panel$param_upper$at),lwd=3,main="Density plot for samples of a=mu*psi") # 
#plot(density(fb_mupsi_panel$param_upper$bt),lwd=3,main="Density plot for samples of b=mu*(1-psi)") # 
plot(fb_mupsi_panel,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",xlab="")
fb_mupsi_panel1=findbetamupsi_panel(themean=c(0.1,0.5,0.05,0.01,0.6,0.65), psi.percentile=0.90,
              percentile.median=0.80, percentile95value=0.90)
lines(fb_mupsi_panel1,main="Elicited beta prior \n(Hierarchical top level)",
              ylab = "Density",lwd=3,type="l",lty=2,col="gray")
legend("topright",c("Panel","Panel1"),col=c("black","gray"),lty=1:2,lwd=3)

```